A generalization of Plackett-Luce likelihoods to incorporate non-independence of competitors

### 2025-03-05 inst/plackett_luce_monster.Rmd
better range
pdftools library not needed

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
library("partitions")
library("pdftools")
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
library("partitions")
```

@@

Now use the evaluate for the likelihood function:

```{r calcmaxmax}
maxHmax <- maxp(RB_BB_LF(s = osup$maximum))
```

```{r showmaxmax}
maxHmax
```
